Pillar 1 - Sequential Pattern Mining

### 2019-01-18 Pillar 1 - Sequential Pattern Mining.Rmd

course_statistics <- exploration %>%
  group_by(`Course ID`) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5)) %>%
  right_join(d_course, by = "Course ID")

@@

cluster_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  group_by(Cluster) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))
```
We have found some NA values for the grades! Students:

>>>>

course_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  filter(between(Year_numerical, 2015,2016)) %>% #filter year
  group_by(`Course ID`) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5)) %>%
  inner_join(select(d_course,`Course ID`, `Course Title`), by = "Course ID")

@@

cluster_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  group_by(Cluster) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

year_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  group_by(Year_numerical) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

level_statistics <- exploration %>%
  inner_join(d_course, by = "Course ID") %>%
  group_by(Level) %>%
  summarise(n = n(),
            Min = min(Grade), 
            Max = max(Grade), 
            Mean = round(mean(Grade), 2), 
            Median = median(Grade), 
            SD = sd(Grade), 
            `Proportion Failed` = mean(Grade < 5.5))

percentage_grades_awarded <- d_transcript %>%
          mutate(Grade = str_replace(string = Grade, pattern = ",",replace = "."),
                 Grade = as.integer(Grade)) %>%
  filter(Year_numerical %in% c(2015,2016))%>%
  mutate(total=n())%>%
  group_by(Grade) %>%
  mutate(grade_total=n())%>%
  select(Grade, grade_total,total)%>%
  distinct()%>%
  mutate(Percentage = signif(grade_total/total,digits=2))%>%
  arrange(Grade)

```
We have found some NA values for the grades! Students:
